---
title: "Worksheet#5a_group"
author: "Cadiz, Guion, Jacildo"
date: "2024-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Extracting Amazon Product Reviews
# 4. Select 5 categories from Amazon and select 30 products from each category.
```{r}
library(rvest)
library(httr)
library(dplyr)
library(polite)
library(kableExtra)
library(rmarkdown)

url <- 'https://www.amazon.com/s?rh=n%3A3760911%2Cn%3A11058281&dc&qid=1730855869&rnid=3760911&ref=sr_nr_n_1i'

session <- bow(url,
               user_agent = "Educational")
session

```
# 5. Extract the price, description, ratings and reviews of each product.
```{r}
page1 <- read_html(url)
price1 <- scrape(session) %>%
  html_nodes('.a-price .a-offscreen') %>% 
  html_text

data1 <- data.frame(
    priceDf1 = price1[1:30])

data1

description1 <- page %>% html_nodes('span.a-size-large product-title-word-break') %>% html_text()

data2 <- data.frame(
    desDf1 = description1[1:30])

data2

ratings1 <- scrape(session) %>%
  html_nodes('span.a-icon-alt') %>% 
  html_text

data3 <- data.frame(
    ratingDf1 = ratings1[1:30])

data3

reviews1 <- scrape(session) %>%
  html_nodes('#acrCustomerReviewText') %>% 
  html_text

data4 <- data.frame(
    reviewsDf1 = reviews1[1:30])

data4
```
# 6. Describe the data you have extracted.
```{r}
library(psych)
describe(data1)
```


# 7. What will be your use case for the data you have extracted?
# 8. Create graphs regarding the use case. And briefly explain it.
# 9. Graph the price and the ratings for each category. Use basic plotting functions and ggplot2 package.
# 10. Rank the products of each category by price and ratings. Explain briefly