---
title: "Worksheet#5a_group"
author: "Cadiz, Guion, Jacildo"
date: "2024-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

# It will also include the number of user reviews and the number of critic reviews, as well as the popularity rating for each tv shows.
```{r}
library(rvest)
library(httr)
library(dplyr)
library(polite)
library(kableExtra)
library(rmarkdown)

url_Imdb <- 'https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250'

sesh <- bow(url_Imdb,
               user_agent = "Educational")
sesh
```
```{r}
library(rvest)
library(dplyr)

title <- character(0)
rank <- character(0)
rating <- character(0)

title <- scrape(sesh) %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text


dataB <- data.frame(
    titleDf = title[1:50])

dataB

colnames(dataB) <- "ranks"

split_df <- strsplit(as.character(dataB$ranks),".",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))

colnames(split_df) <- c("ranks","title")

head(split_df)






```












# Extracting Amazon Product Reviews
# 4. Select 5 categories from Amazon and select 30 products from each category.
```{r}
library(rvest)
library(httr)
library(dplyr)
library(polite)
library(kableExtra)
library(rmarkdown)

url <- 'https://www.amazon.com/s?rh=n%3A3760911%2Cn%3A11058281&dc&qid=1730855869&rnid=3760911&ref=sr_nr_n_1i'

session <- bow(url,
               user_agent = "Educational")
session

```
# 5. Extract the price, description, ratings and reviews of each product.
```{r}
library(rvest)

page1 <- read_html(url)
price1 <- scrape(session) %>%
  html_nodes('.a-price .a-offscreen') %>% 
  html_text

data1 <- data.frame(
    priceDf1 = price1[1:30])

data1

description1 <- page1 %>% html_nodes('span.a-size-large product-title-word-break') %>% html_text()

data2 <- data.frame(
    desDf1 = description1[1:30])

data2

ratings1 <- scrape(session) %>%
  html_nodes('span.a-icon-alt') %>% 
  html_text

data3 <- data.frame(
    ratingDf1 = ratings1[1:30])

data3

reviews1 <- scrape(session) %>%
  html_nodes('#acrCustomerReviewText') %>% 
  html_text

data4 <- data.frame(
    reviewsDf1 = reviews1[1:30])

data4

```
# 6. Describe the data you have extracted.
```{r}
library(psych)
describe(data1)
```


# 7. What will be your use case for the data you have extracted?
# 8. Create graphs regarding the use case. And briefly explain it.
# 9. Graph the price and the ratings for each category. Use basic plotting functions and ggplot2 package.
# 10. Rank the products of each category by price and ratings. Explain briefly