---
title: "Sentiment-Analysis"
author: "Cadiz, Guion, Jacildo"
date: "2024-12-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## LOAD PACKAGES 
```{r}
library(dplyr)
library(tm)
library(tidytext)
library(lubridate)


tweetsDF <- read.csv("tweetsDF.csv")
```
## DATA CLEANING
```{r}
tweetsDF$text <- iconv(tweetsDF$text, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")
tweetsDF$text <- tolower(tweetsDF$text)
tweetsDF$text <- gsub("https\\S+", "", tweetsDF$text)
tweetsDF$text <- gsub("#", "", gsub("\n", " ", tweetsDF$text))
tweetsDF$text <- gsub("([@?]\\S+)", "", tweetsDF$text)
tweetsDF$text <- gsub("\\?", "", tweetsDF$text)
tweetsDF$text <- gsub("\\b\\d{2}\\.\\d{2}\\.\\d{4}\\b", "", tweetsDF$text)
tweetsDF$text <- gsub("<a href=httptwitter.comdownloadiphone rel=nofollow>twitter for iphone<a>", "", tweetsDF$text)
tweetsDF$text <- gsub("<a href=([^>]*?) rel=nofollow>([^<]*?)<a>", "", tweetsDF$text)
tweetsDF$text <- gsub("<a href=httptwitter.comdownloadandroid rel=nofollow>twitter for android<a>", "", tweetsDF$text)
tweetsDF$text <- gsub("<a href= rel=nofollow>twitter web app<a>", "", tweetsDF$text)
tweetsDF$text <- gsub("30102022", "", tweetsDF$text)
tweetsDF$text <- gsub("\\s+", " ", tweetsDF$text)
```


## TREND ANALYSIS

For our trend analysis, we used the 'created' column and the number of tweets 
to generate a line graph. The 'created' column provides the date and time each 
tweet was posted. Our goal was to identify periods of peak activity and explore
the potential reasons behind these trends. We also plan to search for articles 
online to investigate what might have caused the spikes in tweet activity after
the tragedy.
```{r}
library(ggplot2)
library(lubridate)
library(dplyr)

file_path <- "tweetsDF.csv"
tweets_df <- read.csv(file_path)

tweets_df$created <- ymd_hms(tweets_df$created)

tweets_per_time <- tweets_df %>%
mutate(hour = floor_date(created, "hour")) %>%
count(hour)

ggplot(tweets_per_time, aes(x = hour, y = n)) +
geom_line(color = "blue") +
labs(title = "Number of Tweets Over Time", x = "Time", y = "Number of Tweets") +
theme_minimal()
```

The graph shows that tweets about Itaewon were few before midnight on 
October 29. A noticeable spike occurred after midnight, with the highest 
activity in the early hours of October 30. Activity levels decreased throughout 
the morning but rose again in the afternoon and evening.

Upon researching the timeline of events, we discovered that the Itaewon tragedy
occurred at 10:30 PM on October 29. Reports indicate that the police confirmed 
the death toll at 2:30 AM, which likely contributed to the early morning peak in
tweets.The rise in the evening may be due to more people becoming aware of and 
talking about the tragedy.


## SENTIMENT ANALYSIS

The dataset contains tweets about the Itaewon tragedy in 2022 under the 
‘text’ column. We aim to analyze the sentiment of these tweets to understand 
public reactions. By categorizing sentiments as either positive or negative and
visualizing them, we can determine the overall tone of the conversations and 
explore how people responded emotionally to the event. 

```{r}
library(tidytext)
library(dplyr)

sentiments <- get_sentiments("bing")

tweet_tokens <- tweetsDF %>%
unnest_tokens(word, text) %>%
inner_join(sentiments, by = "word")

sentiment_counts <- tweet_tokens %>%
count(sentiment) %>%
mutate(percentage = n / sum(n) * 100)

print(sentiment_counts)

library(ggplot2)
ggplot(sentiment_counts, aes(x = sentiment, y = percentage, fill = sentiment)) +
geom_bar(stat = "identity") +
labs(title = "Sentiment Analysis", x = "Sentiment", y = "Percentage") +
theme_minimal()
```

For our graph, the x-axis represents the sentiment categories 
(negative and positive), while the y-axis represents the percentage of tweets 
in each category. The bar graph indicates a higher percentage of negative tweets
compared to positive ones. That highlights that the majority of tweets are 
negative. This indicates a strong emotional reaction to the event, possibly 
driven by distress, outrage, or grief.


## ADDITIONAL GRAPH

The dataset contains tweets categorized by their source platforms, such as 
iPhone, Android, and others.For additional information, we wanted to identify 
which platforms users mostly used to engage with the content. 
```{r}
tweet_source_analysis <- tweets_df %>%
group_by(tweetSource) %>%
summarise(Number_of_Tweets = n()) %>%
arrange(desc(Number_of_Tweets))


ggplot(tweet_source_analysis, aes(x = reorder(tweetSource, -Number_of_Tweets), y = Number_of_Tweets)) +
geom_bar(stat = "identity", fill = "skyblue") +
labs(
title = "Number of Tweets by Tweet Source",
x = "Tweet Source",
y = "Number of Tweets"
) +
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The bar graph visualizes the number of tweets categorized by their source.
The x-axis represents the tweet sources (e.g., iPhone, Android, others), while 
the y-axis shows the total number of tweets from each sourceThe bars indicate 
the volume of tweets contributed by each platform, with iPhone and Android 
having significantly higher counts than other sources.

